%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Hardy Sandhu} % Your name
\address{2383 Virginia St.} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{559-916-1378 
\\ hdsandhu@berkeley.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Berkeley} \hfill {\em August 2017 - Present} 
\\ Undergraduate, Intended Grad: 2021 \hfill { Overall GPA: 3.4}
\\ Intended Bachelor of Arts, Economics  
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  R, Python, MATLAB \\
Software \& Tools & HTML, LaTeX, Excel, Photoshop, Illustrator, INTUIT Quickbooks \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work \& Experience}

\begin{rSubsection}{FYZICAL Therapy}{June 2017 - July 2017}{Therapist Assistant}{}
\item -Articulated spreadsheets for patient work out and exercise plans.
\item -Organized and planned schedule for Head Physical Therapist in the clinic, planned patienst time slots.
\item -Handled insurance information and screenings within the clinic for patients.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Redrock Management}{January 2012 - August 2017}{Operations Manager}{}
\item -Filed payroll for roughly 12 employees and compiled on a quarterly basis. 
\item -Submitted chemical use reports and established spreadsheets for crop yields through delivery data, while assessing performances of different varieties.
\item -Managed day to day operations of crop operations such as: pruning, irrigating, and harvesting.
\end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Extracirriculars \& Hobbies} \itemsep -2pt
\item -Avid gamer involved in aspects of competitive gaming and esports on the Cal campus. 
\item -Computer Science Undergraduate Association member partaking in involving any Cal student interested in CS in order to foster a helpful and productive family environment.
\item -Member of the University of California Rally Committee which indulges school spirit and appreciation towards the various athletic programs at Cal by organizing various game day and week activities to increase school spirit. 
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\itab{\textbf{Personal Skills}} \tab{}  \tab{\textbf{Work Skills}}
\\ \itab{Responsible } \tab{}  \tab{Work Well Under Pressure}
\\ \itab{Respectful} \tab{}  \tab{Goal-oriented} 
\\ \itab{Attentive} \tab{}  \tab{Self-motivated} 
\\ \itab{Humorous} \tab{} \tab{Active Listening}
\\ \itab{Passionate} \tab{} \tab{Management \& Leadership skills}
% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

\end{rSection}


\end{document}
